Analysis

### 2019-04-26 reports/DRM_exp/analysis_DRM_exp1.Rmd
add classical dprime analysis

```{r}
trial_ids <- df_acc %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

@@

df_acc2 <- df_acc %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

@@

@@

>>>>

```{r}
trial_ids <- df %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

@@

df_acc2 <- df %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

@@

```{r two dprimes and bias}
df_dprime2 <- df %>% 
  group_by(subject_id) %>% 
  summarize(H = sum(key_resp == "old" & corrKey == "old")/(sum(corrKey == "old")),
            FA_close = sum(key_resp == "old" & corrKey == "new" & type == "close distractor")/(sum(corrKey == "new" & type == "close distractor")),
            FA_far = sum(key_resp == "old" & corrKey == "new" & type == "far distractor")/(sum(corrKey == "new" & type == "far distractor"))) %>% 
  mutate(d_oldclose = qnorm(H) - qnorm(FA_close),
         d_oldfar = qnorm(H) - qnorm(FA_far),
         c_oldclose = -0.5*(qnorm(H) + qnorm(FA_close)),
         c_oldfar = -0.5*(qnorm(H) + qnorm(FA_far)))
t.test(df_dprime2$d_oldclose, df_dprime2$d_oldfar)
t.test(df_dprime2$c_oldclose, df_dprime2$c_oldfar)  
colMeans(df_dprime2)
```

@@

# Memorability

Memorability were computed using pretrained CNN

```{r load mem data}
mem_imgnames <- read_csv(here::here("data/exp_DRM1/memorability/memorability_imgnames.txt"), col_names = F)
mem_values <- read_csv(here::here("data/exp_DRM1/memorability/memorability_all.txt"), col_names = F)

df_mem <- tibble(img_name = mem_imgnames$X1, mem_score = mem_values$X1)
dfm <- df %>% left_join(df_mem,by = "img_name")

cor.test(~correct+mem_score, dfm %>% filter(type == "target"))
cor.test(~correct+mem_score, dfm %>% filter(type == "close distractor"))
cor.test(~correct+mem_score, dfm %>% filter(type == "far distractor"))
```

# Per image accuracy

```{r }
df %>% group_by(img_name,type) %>% summarize(m = mean(correct), sd = sd(correct)) %>% arrange(-m)
```
